Combining information from photometric and spectroscopic data:\\ Don't waste your time in spectrophotometric calibration!

### 2014-07-28 tex/ms.tex
minor tweak

The physical model parameters that we infer indicate that \excluster~
has super-solar metallicity, an age of $\sim 225$ Myr, moderate dust
extinction, and a stellar mass of $\sim 1e5$ M$_{sun}$ {\color{blue}
check that this is current mass, not initial mass}.  We find a spectral
broadening of $\sim 1.75$\AA (4.1\AA FWHM), which when combined in
quadrature with the intrinsic resolution of the MILES library, 2.5\AA
FWHM \citep{beifiori11}, reproduces the typical line-spread function
of the MMT Hectospec instrument, $\sim 5.0$\AA \citep{fabricant13}.
We obtain strong constraints on the systemic velocity.

For the calibration model, we obtain a calibration vector $f(\alpha)$
that is nearly linear in wavelength {\color{red} WHY IS IT NOT A
CONSTANT?  Need longer burn-in?  Is this the same issue as the SED
residuals?}.  The length scale of the Gaussian process is $\sim
60$\AA.  It is possible to reconstruct the inferred total
multiplicative calibration vector for each draw of the model
parameters.  Rearranging equation \ref{eq:spectroscopicLF} yields
\begin{eqnarray} 
\frac{d}{\mu(\theta)} & = & f(\alpha) +
\frac{\tilde{\Delta}}{\mu(\theta)}
\quad ,
\end{eqnarray}
for the total effective multiplicative calibration, where
$\tilde{\Delta}$ is now the Gaussian process mean prediction for the
residual between the data and the model. The inverse of this ratio is
shown in the left panel of Figure \ref{fig:inferred_calib} as our
inferred total multiplicative calibration function; if the
spectrophotometric calibration were perfect and we had correctly
inferred it, then we would expect this vector to be constant as a
function of wavelength.

>>>>

The physical model parameters that we infer indicate that \excluster~
has super-solar metallicity, an age of $\sim 225$ Myr, moderate dust
extinction, and a stellar mass of $\sim 10^{4}$ M$_{sun}$ {\color{blue}
check that this is current mass, not initial mass}.  We find a spectral
broadening of $\sim 1.75$\AA (4.1\AA FWHM), which when combined in
quadrature with the intrinsic resolution of the MILES library, 2.5\AA
FWHM \citep{beifiori11}, reproduces the typical line-spread function
of the MMT Hectospec instrument, $\sim 5.0$\AA \citep{fabricant13}.
We obtain strong constraints on the systemic velocity.

For the calibration model, we obtain a vector $f(\alpha)$
that is nearly linear in wavelength {\color{red} WHY IS IT NOT A
CONSTANT?  Need longer burn-in?  Is this the same issue as the SED
residuals?}.  The length scale of the Gaussian process is $\sim
60$\AA.  It is possible to reconstruct the inferred total
multiplicative calibration vector for each draw of the model
parameters.  Rearranging equation \ref{eq:spectroscopicLF} yields
\begin{eqnarray} 
\frac{d}{\mu(\theta)} & = & f(\alpha) +
\frac{\tilde{\Delta}}{\mu(\theta)}
\quad ,
\end{eqnarray}
for the total effective multiplicative calibration, where
$\tilde{\Delta}$ is now the Gaussian process mean prediction for the
residual between the data and the model. The inverse of this ratio is
shown in the left panel of Figure \ref{fig:inferred_calib} as our
inferred total multiplicative calibration function; if the
spectrophotometric calibration were perfect and we had correctly
inferred it, then we would expect this vector to be constant as a
function of wavelength.
